### 2021-03-23 Chapter-1/Chapter-1.tex
Updates from Overleaf

>>>>

The key intuition is that above side-channel attacks happen when a
program accesses different memory addresses if the program has different
sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
if a program shows different patterns in
control transfers or data accesses when the program processes different
sensitive inputs, the program could possibly have side channels vulnerabilities.
Different kinds of side-channels can be exploited to retrieve information in
various granularities. For example, cache channels can observe cache
accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
Other kinds of side-channels like controlled-channel attack~\cite{7163052},
can observe the memory access at the level of memory pages.

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Side-channel Attacks}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

Side channels can leak sensitive information
unconsciously through different execution behaviors caused by shared 
hardware components (e.g., CPU cache, TLB, and
DRAM) in modern computer system~\cite{ge2018survey,szefer2019survey}.

@@

The key intuition is that above side-channel attacks happen when a
program accesses different memory addresses if the program has different
sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
if a program shows different patterns in
control transfers or data accesses when the program processes different
sensitive inputs, the program could possibly have side channels vulnerabilities.
Different kinds of side-channels can be exploited to retrieve information in
various granularities. For example, cache channels can observe cache
accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
Other kinds of side-channels like controlled-channel attack~\cite{7163052},
can observe the memory access at the level of memory pages.

>>>>

\section{Side-channel Attacks}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

\begin{table}
\centering
\caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
\label{table:side_channel_attack}
\resizebox{\columnwidth}{!}{%

@@
